\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{\Huge \textbf{Design Specifications}\\[6pt]
    {\LARGE Sleep Fixer App}\\[10mm]
    {\Large Group 6}}
\author{Dang Nguyen \and Rafael Caldera \and Yohei Oya \and Yuanwei Chen}
\date{December 2025}

\begin{document}

\maketitle

\section*{Packages}

\section*{Dependencies}

\subsection*{Front-End (Flutter)}
\begin{itemize}
    \item \textbf{Flutter SDK (3.x):} Core cross-platform UI framework used to build iOS, Android, and Web versions of the Sleep Fixer app.
    \item \textbf{Dart Language:} Compiled language used by Flutter for UI and business logic.
    \item \textbf{Hive (Local NoSQL Database):}  
    Lightweight database used for:
    \begin{itemize}
        \item user sleep plan storage,
        \item daily progress tracking,
        \item user preferences.  
    \end{itemize}
    Dependencies:
    \begin{itemize}
        \item \texttt{hive}
        \item \texttt{hive\_flutter}
        \item \texttt{path\_provider}
    \end{itemize}

    \item \textbf{Provider (State Management):}  
    Used to manage UI state for:
    \begin{itemize}
        \item onboarding flow,
        \item plan creation,
        \item progress updates,
        \item insights display.
    \end{itemize}

    \item \textbf{Flutter Local Notifications:}  
    Supports Snapshot 2 features:
    \begin{itemize}
        \item bedtime reminders,
        \item morning check-in prompts.
    \end{itemize}
    Dependency:
    \begin{itemize}
        \item \texttt{flutter\_local\_notifications}
    \end{itemize}

    \item \textbf{Intl Package:}  
    Supports formatting sleep times, dates, weekly reports.

    \item \textbf{Firebase Framework (Snapshot 3 – Community \& Cloud Sync):}
    Used for:
    \begin{itemize}
        \item anonymous community posts,
        \item monthly challenges,
        \item optional cloud backup of sleep data,
        \item user authentication.
    \end{itemize}
    Dependencies:
    \begin{itemize}
        \item \texttt{firebase\_core}
        \item \texttt{firebase\_auth}
        \item \texttt{cloud\_firestore}
    \end{itemize}

    \item \textbf{Accessibility Support (Snapshot 4):}
    \begin{itemize}
        \item dynamic text resizing,
        \item screen reader compatibility.
    \end{itemize}
\end{itemize}

\subsection*{Back-End (Snapshot 3 -- Firebase Services)}
Although Sleep Fixer does not use a traditional custom backend, Snapshot 3 introduces a cloud component for social features and storage.

\begin{itemize}
    \item \textbf{Firebase Authentication:}  
    Provides anonymous or optional user login for community features.
    
    \item \textbf{Cloud Firestore:}  
    Stores:
    \begin{itemize}
        \item community posts,
        \item challenge participation data,
        \item optional backups of local sleep data.
    \end{itemize}
    
    \item \textbf{Firebase Functions (Optional):}  
    Supports leaderboard logic or scheduled insights generation.

    \item \textbf{Firebase Storage (Optional):}  
    Used only if users upload journal attachments (future work).
\end{itemize}

\subsection*{Database Management}
\begin{itemize}
    \item \textbf{Hive Local Database (Primary Storage):}
    \begin{itemize}
        \item Sleep plan configuration
        \item Daily progress entries
        \item User preferences
    \end{itemize}
    Stored on-device with:
    \begin{itemize}
        \item no internet needed,
        \item fast read/write performance.
    \end{itemize}

    \item \textbf{Cloud Firestore (Snapshot 3 Feature):}
    \begin{itemize}
        \item Backup solution,
        \item Community data storage,
        \item Cross-device sync of streaks or achievements.
    \end{itemize}
\end{itemize}

\section*{Libraries}

\begin{itemize}
    \item \textbf{Flutter Material Library} – Core UI components used throughout the app.
    \item \textbf{Provider} – Lightweight state management for dynamic screens.
    \item \textbf{Hive} – Local NoSQL storage library for sleep plans and progress.
    \item \textbf{firebase\_core, firebase\_auth, cloud\_firestore} – Cloud features used from Snapshot 3 onward.
    \item \textbf{flutter\_local\_notifications} – Supports bedtime reminders.
    \item \textbf{intl} – Formatting of time, dates, and weekly reports.
\end{itemize}

\end{document}
